---
title: "Exploring the data"
author: "Danielle Navarro"
date: "4 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting started

The first thing to do in our analysis is load the R
packages that we'll use to do the work:

```{r packageload, message=FALSE}
library(here)
library(tidyverse)
library(skimr)
```

The next step is to load the data set itself. The data 
from the sampling frames experiment are stored in the 
"frames_ex2.csv" file:

```{r dataimport}
loc <- here("analysis","data","frames_ex2.csv")
frames <- read_csv(file = loc)
```

The data set has been imported as a tibble. Let's take 
a quick look at the data. Each row in the data set is
a single response, and each column is a variable:

```{r printframes}
frames
```

An alternative way to view the a tibble that sometimes
looks nicer is to use the `glimpse()` function:

```{r glimpseframes}
glimpse(frames)
```

Finally, as a quick first pass, we can use the `skim()`
function to get a simple overview of each variable:

```{r skimframes}
skim(frames)
```
